Detecting Facial Expressions in Professional Tennis Matches

### 2017-02-16 Report06-12.Rmd

#csv files:
ALLmetaIMG<-read_csv("ALLmetaIMG1.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")
FaceAttributes<-read_csv("TableCSVs/FaceAttributes.csv")
SolutionSpecs<-read_csv("TableCSVs/SolutionSpecifications.csv")

>>>>

#csv files:
ALLmetaIMG<-read_csv("ALLmetaIMG.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")
FaceAttributes<-read_csv("TableCSVs/FaceAttributes.csv")
SolutionSpecs<-read_csv("TableCSVs/SolutionSpecifications.csv")
